### 2020-05-27 sc20_reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

Changes made in response to reviewer comments:

Responding to reviewer questions:

### 2020-05-27 8_case_study.tex
Some more text on case study.

Task Bench is useful not only as a tool for evaluating programming
system performance, but also for discovering potential areas for
improvement. During the development of Task Bench, we identified a
number of performance issues in the underlying programming
systems. These discoveries were possible because of the flexibility of
Task Bench, and our ability to rapidly run new experiments with a
variety of application scenarios. All issues were reported to and
acknowledged by the respective system's developers, and are either
fixed or worked around in our experiments. For brevity, we describe
one salient example below and summarize the others briefly.

@@

We found further areas for improvement in schedulers (Realm, Chapel
and Dask), task pruning for scalability (PaRSEC), and optimizations on
the task graph (TensorFlow). The impact of these optimizations ranged
from small constant factors to even asymptotic improvements in
performance and scalability (in the case of PaRSEC and Dask). All
users will benefit from the improvements driven by our discoveries.

\zap{
Further analysis of Realm efficiency indicated many overheads due to
dynamic graph construction. The Realm developers implemented a new
``subgraph'' API in response to this feedback to amortize the cost of
repeatedly constructing isomorphic task graphs. This API is used in
Task Bench to achieve further speedups in the Realm implementation.

@@

PaRSEC uses task pruning to improve scalability at large node
counts. Initial Task Bench results achieved less than the expected
scalability: METG was rising too quickly with node count.  The PaRSEC
developers diagnosed this as a bug in task pruning, and it was
subsequently fixed. We also implemented a version of the PaRSEC code,
\lstinline{shard}, which uses manual pruning to demonstrate that
additional gains may be possible.

Early Task Bench results for Dask revealed that the cost of scheduling
a task was $\mathcal{O}(N)$ where $N$ is the number of tasks in a task
graph, causing overall cost for a task graph with $N$ nodes to be
$\mathcal{O}(N^2)$. This issue was reported to and confirmed by the
Dask developers. As a work around, our results in the paper use a
lower-level interface which does not suffer from this asymptotic
slowdown.

Initial experiments with TensorFlow revealed that the TensorFlow Task
Bench implementation was not able to use all cores on a node (thus
making it impossible to measure METG since the efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.
}

>>>>

Task Bench is useful not only as a tool for evaluating programming
system performance, but also for discovering potential areas for
improvement. During the development of Task Bench, we identified a
number of performance issues in the underlying programming
systems. These discoveries were possible because of the flexibility of
Task Bench, and our ability to rapidly run new experiments with a
variety of application scenarios. All issues were reported to and
acknowledged by the respective system's developers, and are either
fixed or worked around in our experiments. We describe them below.

@@

{\color{blue}
Further analysis of Realm efficiency indicated many overheads due to
dynamic graph construction. The Realm developers implemented a new
``subgraph'' API in response to this feedback to amortize the cost of
repeatedly constructing isomorphic task graphs. This API is used in
Task Bench to achieve further speedups in the Realm implementation.

@@

PaRSEC uses task pruning to reduce analysis work performed on each
node, and thus improve scalability at large node
counts. Initial Task Bench results achieved less than the expected
scalability: METG was rising too quickly with node count.  The PaRSEC
developers diagnosed this as a bug in task pruning---the optimization was failing to trigger---and it was
subsequently fixed. We also implemented a version of the PaRSEC code,
\lstinline{shard}, which uses manual pruning to demonstrate that
additional gains may still be possible.

Early Task Bench results for Dask revealed that the cost of scheduling
a task was $\mathcal{O}(N)$ where $N$ is the number of tasks in a task
graph, causing overall cost for a task graph with $N$ nodes to be
$\mathcal{O}(N^2)$. This issue was reported to and confirmed by the
Dask developers; the bug is suspected to be in optimizations performed
on the task graph by Dask. As a work around, our results in the paper use a
lower-level interface which does not suffer from this asymptotic
slowdown.

Initial experiments with TensorFlow revealed that the TensorFlow Task
Bench implementation was not able to use all cores on a node (thus
making it impossible to measure METG since the efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.

In all cases, we found bugs that are applicable outside of Task Bench
and that impact metrics other than METG. Notably, the scalability
issues and asymptotic complexity have a growing impact with larger
node counts and will eventually become visible with nearly any
application. In other cases, we found performance degradation at the
extremes of application configurations which may be more difficult to
test with full-size applications, but which are nonetheless relevant
in strong-scaling regimes, particularly as node counts grow.

} % color

\zap{
We found further areas for improvement in schedulers (Realm, Chapel
and Dask), task pruning for scalability (PaRSEC), and optimizations on
the task graph (TensorFlow). The impact of these optimizations ranged
from small constant factors to even asymptotic improvements in
performance and scalability (in the case of PaRSEC and Dask). All
users will benefit from the improvements driven by our discoveries.
} % zap
